---
title: "R Workshop 2024"
subtitle: "<i>BMC YMH Team</i>"  
author: 
  - "Timothy Wong"
date: 'Spring 2024'
output:
  xaringan::moon_reader:
    css: ["cols.css", "xaringan-themer.css"]
    nature:
      beforeInit: "cols_macro.js"
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
blue <- "#1381B0"
orange <- "#FF961C"
white <- "#FFFFFF"


style_duo_accent(
  primary_color = blue,
  secondary_color = orange,
  inverse_header_color = white,
  text_bold_color = orange,
  
  # Custom
  title_slide_background_color = white,
  title_slide_text_color = blue
)
```

name: housekeeping

## Housekeeping

1. Did you bring a laptop (Mac or Windows)?

2. Have you downloaded R and RStudio?

3. Have you downloaded XCode (Mac) or Rtools (Windows)?

If are stuck on Step 2 or 3, **please let us know now**
---
name: colors

## Overview

1. What is R?

2. The RStudio interface

3. Objects and functions

4. Packages

5. Reading in files and the working directory

6. Manipulating data using `tidyverse`

---
class: inverse center middle

# What is R?

---

name: why R

## Why use R?

.pull-left[
### Pros

* Free

* Open-source

* Huge community of experts

* Is a *language* (more on this later)

]

.pull-right[
### Cons

* Can be difficult to pick up

* Curse of freedom
]

--
<br>

**Thesis**: The pros of learning R outweight the cons

---
name: what R
## What is R?
![:col_header Statistical, programming, language]
![:col_row Regression, , ]
--
![:col_row ANOVA, , ]
--
![:col_row ,Computer instructions , ]

---
class: inverse center middle

# The RStudio interface

---



